---
title: "Visualization of probability density functions of Exponential, Normal, Gamma, t, Cauchy and G-Zero Intensity distributions"
output: html_notebook
---

```{r}
library(ggplot2)
```


### Exponential Distribution

The following is the probability density function characteristic of the Exponential distribution. The random variable $X$ follows an Exponential distribution with parameter $\lambda$  if it has the probability density function below where $\lambda$ must be greater than zero.

```{r}
densExp <- function(x, lambda) {
  
  ifelse(x>=0, (1/lambda) * exp(-x/lambda), 0)
  
}
```

Below are the views of the probability density functions for this distribution. For the generation of the graphs, values 1, 2 and 3 were used for the $lambda$ parameter. The notation used is $X$ ~ $Exp(\lambda)$.

```{r}
x <- seq(from=0.001, to=4, by = 0.001)

dens1 <- densExp(x, 1)
dens2 <- densExp(x, 2)
dens3 <- densExp(x, 3)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Exponencial distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x, dens1, colour="black"), size=1.3) +
  geom_line(aes(x, dens2, colour="blue"), size=1.3) +
  geom_line(aes(x, dens3, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Exp(1)", "Exp(2)", "Exp(3)"))
```

### Normal Distribution

A continuous random variable $X$ has Normal distribution if its probability density function is given by:

```{r}
densNormal <- function (x, mi, sigmaQuad) {
  
  return ((1/sqrt(2*pi*sigmaQuad)) * exp ((-1/(2*sigmaQuad))*(x - mi)^2))
  
}
```

 This case we use the notation $X$ ~ $N(\mu, \sigma^2)$. Below are density plots for this distribution.
 
 
 
```{r}
x <- seq(from=-6, to=6, by = 0.001)

dens1 <- densNormal(x, 0, 1)
dens2 <- densNormal(x, 0, 4)
dens3 <- densNormal(x, 0, 9)
 
qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Normal distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens1, colour="black"), size=1.3) +
  geom_line(aes(x,dens2, colour="blue"), size=1.3) +
  geom_line(aes(x,dens3, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("N(0,1)", "N(0,4)", "N(0,9)"))


dens4 <- densNormal(x, 0, 1)
dens5 <- densNormal(x, 1, 1)
dens6 <- densNormal(x, 1, 4)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Normal distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens4, colour="black"), size=1.3) +
  geom_line(aes(x,dens5, colour="blue"), size=1.3) +
  geom_line(aes(x,dens6, colour="red"), size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("N(0,1)", "N(1,1)", "N(1,4)"))



dens7 <- densNormal(x, 1, 1)
dens8 <- densNormal(x, 2, 1)
dens9 <- densNormal(x, 1, 9)


qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Normal distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens7, colour="black"), size=1.3) +
  geom_line(aes(x,dens8, colour="blue"), size=1.3) +
  geom_line(aes(x,dens9, colour="red"), size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("N(1,1)", "N(2,1)", "N(1,9)"))
```

### Gamma Distribution

A random variable $X$ has Gamma distribution with parameters $\alpha > 0$ (also called shape parameter) and $\beta > 0$ (rate parameter), with notation $X$ ~ $Gamma(\alpha,\beta)$, if its density function is given by

```{r}
densGama <- function (x, alpha, beta) {
 
  ifelse(x>=0, (beta^alpha * x^(alpha-1) * exp(-beta*x))/gamma(alpha),0)
  
}
```


Below are density plots for this distribution.

```{r}
x <- seq(from=0, to=10, by = 0.001)

dens1 <- densGama(x, 2, 0.5)
dens2 <- densGama(x, 2, 1)
dens3 <- densGama(x, 2, 2)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Gama distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens1, colour="black"), size=1.3) +
  geom_line(aes(x,dens2, colour="blue"), size=1.3) +
  geom_line(aes(x,dens3, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Gama(2,1/2)", "Gama(2,1)", "Gama(2,2)"))

dens4 <- densGama(x, 4, 0.5)
dens5 <- densGama(x, 4, 1)
dens6 <- densGama(x, 4, 2)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Gama distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens4, colour="black"), size=1.3) +
  geom_line(aes(x,dens5, colour="blue"), size=1.3) +
  geom_line(aes(x,dens6, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Gama(4,1/2)", "Gama(4,1)", "Gama(4,2)"))


dens7 <- densGama(x, 2, 0.5)
dens8 <- densGama(x, 4, 0.5)
dens9 <- densGama(x, 4, 2)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Gama distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens7, colour="black"), size=1.3) +
  geom_line(aes(x,dens8, colour="blue"), size=1.3) +
  geom_line(aes(x,dens9, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Gama(2,1/2)", "Gama(4,1/2)", "Gama(4,2)"))


```


### t Distribution

A continuous random variable $X$ has Student distribution $t$ with $v$ degrees of freedom if its probability density function is given by:

```{r}
densT <- function(x, v) {
  return  (((gamma((v+1)/2))/(sqrt(v*pi) * gamma(v/2))) * (1 + (x^2/v))^(-1*((v+1)/2)))
}
```

The notation in this case is given by $X$ ~ $t_{v}$. The density function of Student's t distribution has the same shape in bell of the Normal distribution, but reflects the greater variability (with wider curves) than is expected in small samples.

The higher the degree of freedom, the more Student's t distribution approaches the Normal distribution. Below are density plots for this distribution.

```{r}
x <- seq(from=-4, to=4, by = 0.001)

dens1 <- densT(x, 1)
dens2 <- densT(x, 5)
dens3 <- densT(x, 15)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a T distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens1, colour="black"), size=1.3) +
  geom_line(aes(x,dens2, colour="blue"), size=1.3) +
  geom_line(aes(x,dens3, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("t(1)", "t(5)", "t(15)"))
```

### Cauchy Distribution

A continuous random variable $X$ has Cauchy distribution with parameters $\alpha$ and $\beta$ if its probability density function and its distribution function are respectively defined by:

```{r}
densCauchy <- function(x, alpha, beta) {
  
  return (1/(pi*beta*(1 + ((x - alpha)/beta)^2)))
  
}
```

Where $\alpha$ and $\beta$ are location and scale parameters, respectively. Below are density plots for this distribution.

```{r}
x <- seq(from = -5, to = 5, by = 0.001)

dens1 <- densCauchy(x, 0, 4)
dens2 <- densCauchy(x, 0, 2)
dens3 <- densCauchy(x, 0, 1/2)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Cauchy distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens1, colour="black"), size=1.3) +
  geom_line(aes(x,dens2, colour="blue"), size=1.3) +
  geom_line(aes(x,dens3, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Cauchy(alpha=0, beta=4)", "Cauchy(alpha=0, beta=2)", "Cauchy(alpha=0, beta=1/2)"))


dens4 <- densCauchy(x, 0, 2)
dens5 <- densCauchy(x, 2, 2)
dens6 <- densCauchy(x, 2, 1/2)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Cauchy distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens4, colour="black"), size=1.3) +
  geom_line(aes(x,dens5, colour="blue"), size=1.3) +
  geom_line(aes(x,dens6, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Cauchy(alpha=0, beta=2)", "Cauchy(alpha=2, beta=2)", "Cauchy(alpha=2, beta=1/2)"))


dens7 <- densCauchy(x, -2.5, 1/4)
dens8 <- densCauchy(x, 0, 1/3)
dens9 <- densCauchy(x, 2.5, 1/2)

qplot (xlab="x", ylab="density") +
  ggtitle("Probability density function of a Cauchy distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens7, colour="black"), size=1.3) +
  geom_line(aes(x,dens8, colour="blue"), size=1.3) +
  geom_line(aes(x,dens9, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("Cauchy(alpha=-2.5, beta=1/4)", "Cauchy(alpha=0, beta=1/3)", "Cauchy(alpha=2.5, beta=1/2)"))
```

### G-Zero Intensity ($G_I^0$) Distribution

A random variable $X$ follows a G-Intensity Zero distribution with parameters $\alpha$, $\gamma$, and $Looks$, denoted by $X$ ~ $G_I^0(\alpha,\gamma, Looks)$, if its probability density function is defined as follows:

```{r}
densGI0 <- function(x, alpha, gamma, Looks) {
  
  return(((Looks^Looks * gamma(Looks-alpha))/ (gamma^alpha * gamma(Looks) * gamma(-alpha))) *
    (x^(Looks-1) / (gamma + Looks * x)^(Looks-alpha)))
  
}

```

The necessary restrictions in this case are: $\alpha$ < 0 and $\gamma$ > 0. Below are density plots for this distribution.

```{r}
x <- seq(from=0.001, to=4, by = 0.001)


dens1 <- densGI0(x, -3, 2, 1)
dens2 <- densGI0(x, -3, 2, 3)
dens3 <- densGI0(x, -3, 2, 8)

qplot (xlab="Intensity", ylab="GI0 Densities") +
  ggtitle("Probability density function of a GI0 distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens1, colour="black"), size=1.3) +
  geom_line(aes(x,dens2, colour="blue"), size=1.3) +
  geom_line(aes(x,dens3, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("GI0(-3,2,1)", "GI0(-3,2,3)", "GI0(-3,2,8)"))


dens4 <- densGI0(x, -1.5, 0.5, 1)
dens5 <- densGI0(x, -3, 2, 1)
dens6 <- densGI0(x, -8, 7, 1)

qplot (xlab="Intensity", ylab="GI0 Densities") +
  ggtitle("Probability density function of a GI0 distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens4, colour="black"), size=1.3) +
  geom_line(aes(x,dens5, colour="blue"), size=1.3) +
  geom_line(aes(x,dens6, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("GI0(-1.5,0.5,1)", "GI0(-3,2,1)", "GI0(-8,7,1)"))


dens7 <- densGI0(x, -1.5, 0.5, 3)
dens8 <- densGI0(x, -3, 2, 3)
dens9 <- densGI0(x, -8, 7, 3)

qplot (xlab="Intensity", ylab="GI0 Densities") +
  ggtitle("Probability density function of a GI0 distribution") +
  theme(plot.title = element_text(hjust=0.5)) +
  geom_line(aes(x,dens7, colour="black"), size=1.3) +
  geom_line(aes(x,dens8, colour="blue"), size=1.3) +
  geom_line(aes(x,dens9, colour="red") , size=1.3) +
  scale_color_discrete(name = "parameters", labels = c("GI0(-1.5,0.5,3)", "GI0(-3,2,3)", "GI0(-8,7,3)"))

```
























